Jane, John … Leslie? A Historical Method for Algorithmic Gender Detection

### 2014-09-19 article.Rmd
Lunbeck citation

In a 2005 report for the American Historical Association, Elizabeth Lunbeck acknowledged "a sea change in the [historical] profession with respect to gender" before going on to describe the painful limitations of this sea change for female historians: ongoing personal discrimination, lower salaries, and barriers to securing high-ranking positions. Lunbeck's report drew in part on a survey of 362 female historians that produced a rich source of responses detailing the deep and multi-faceted challenges facing women in the profession. What follows is a quantitative supplement to Lunbeck's analysis that uses our program to analyze gender representation amongst historians across a much larger scale and a much longer time period.^[http://www.historians.org/Documents/About%20AHA%20and%20Membership/CWH-Report_5.20.05.pdf]

@@

>>>>

In a 2005 report for the American Historical Association, Elizabeth Lunbeck acknowledged "a sea change in the [historical] profession with respect to gender" before going on to describe the painful limitations of this sea change for female historians: ongoing personal discrimination, lower salaries, and barriers to securing high-ranking positions. Lunbeck's report drew in part on a survey of 362 female historians that produced a rich source of responses detailing the deep and multi-faceted challenges facing women in the profession [Lunbeck 2005]. What follows is a quantitative supplement to Lunbeck's analysis that uses our program to analyze gender representation amongst historians across a much larger scale and a much longer time period.

@@

[Lunbeck 2005] Lunbeck, Elizabeth, et al. The Status of Women in the Historical Profession. American Historical Association Committee on Women Historians (2005): http://www.historians.org/Documents/About%20AHA%20and%20Membership/CWH-Report_5.20.05.pdf.
